\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{microtype}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\title{\textbf{Preregistered QRNG Drift Protocol for MQGT-SCF Theorem-1}\\
\large A fixed-$N$, permutation-controlled test}
\author{Christopher Michael Baird\\ \small \texttt{[contact]}}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a preregistered protocol to test whether an ``aligned'' condition produces statistically detectable drift in a QRNG bitstream relative to neutral and shuffled-label controls. The analysis is fixed-$N$, includes permutation testing, and is designed to survive adversarial peer review. The protocol is compatible with MQGT-SCF-style biased collapse models but does not assume their correctness.
\end{abstract}

\section{Model}
Binary outcomes $x\in\{0,1\}$ with baseline $|c_0|^2=|c_1|^2=\tfrac12$. Biased model:
\[
P(1)=\frac{1}{1+\exp((E_1-E_0)/C)}.
\]
Effect size: $\delta=P(1)-\tfrac12$.

\section{Conditions}
A (Aligned), B (Neutral), C (Shuffled-label placebo). Analyst blinded to labels until preprocessing and QC complete.

\section{Stopping rule}
Fixed $N_A=N_B=10^6$ bits minimum per condition. No interim peeking.

\section{Primary statistic}
\[
\Delta_{A-B}=\bar{x}_A-\bar{x}_B,\quad
Z_{A-B}=\frac{\Delta_{A-B}}{\sqrt{\frac{1}{4N_A}+\frac{1}{4N_B}}}.
\]
Threshold: $|Z_{A-B}|\ge 2.58$ (two-sided $\alpha=0.01$).

\section{Permutation test}
10,000 label permutations; require observed $|\Delta_{A-B}|$ exceed 99th percentile of permutation null.

\section{Falsifiers}
No support if $|Z_{A-B}|<2.58$ or permutation fails or placebo reproduces the effect.

\appendix
\section{Full prereg text}
\begin{verbatim}
[Insert OSF prereg text here verbatim.]
\end{verbatim}

\end{document}
